---
title: "Exc3B - Roads in Europe"
author: "Ido Algom & Natalie Gilboa"
output: html_document
---

This dataset shows each pair of cities that have a direct road between them
Source: http://konect.uni-koblenz.de/networks/

```{r, message=FALSE, warning=FALSE}
library(igraph)
require(igraph)
```

Load The Data set: 

```{r Intro}
eue.data = read.csv('eur.csv',header = F)
eur_data =  graph.data.frame(eue.data,directed = F)
```

Remove self loops:

```{r Remove Self loops}
eur_data = simplify(eur_data)
```

# Centrality Degree

## Betweeness

```{r Betweeness1-Prep}
bet = betweenness(eur_data)
bet = sort(bet,decreasing = T)
```
```{r Betweeness1-Res}
names(bet[1])
```

## Closeness 

```{r Closeness1-Prep}
close = closeness(eur_data)
close = sort(close, decreasing = T)
```
```{r Closeness1-Res}
names(close[1])
```

## Eigenvector
```{r Eigenvector1-Prep}
eigen = evcent(eur_data)
eigen = sort(eigen$vector, decreasing = T)
```
```{r Eigenvector1-Res}
names(eigen[1])
```

# Community Detection

We started the algorithms: 

1. Girvan-Newman
2. Multi-Level

## Girvan-Newman

```{r Girvan-Newman}
girvan = edge.betweenness.community(eur_data)
```

```{r Girvan-Newman-Plot}
membership_girvan = membership(girvan)
plot(eur_data, vertex.size=7, vertex.label=NA,vertex.color=membership_girvan, asp=FALSE)
```

## Community recived and their size

```{r Girvan-Newman-Community}
max(levels(as.factor(membership_girvan)))
```
```{r Girvan-Newman-Sum}
summary(as.factor(membership_girvan))
```

## Modularity
```{r Girvan-Newman-Mod}
girvan$modularity
```

# Multi-Level

```{r Multi-Level}
multi = multilevel.community(eur_data)
```

```{r Multi-Level-Plot}
membership_multi = membership(multi)
plot(eur_data, vertex.size=7, vertex.label=NA,vertex.color=membership_multi, asp=FALSE)
```

## Community recived and their size

```{r Multi-Level-Comm}
max(levels(as.factor(membership_multi)))
```
```{r Multi-Level-Sum}
summary(as.factor(membership_multi))
```

## Modularity
```{r Multi-Level-Mod}
multi$modularity
```

